### 2019-11-22 2_task_bench.tex
Uncapitalize after colon.

\zap{
Despite its generality, Task Bench is easy to implement, making it
tractable to develop a suite of high-quality implementations. The central aspects of Task Bench, such as generating
task graphs and enumerating dependencies, are encapsulated in a core
library that is shared among all the Task Bench implementations. The
core library also includes implementations of the kernels, ensuring
that the kernels are identical in all systems, eliminating a potential
source of performance disparity that can be a pitfall for
implementations of mini-apps. Finally, the core library manages
parsing input parameters and displaying results,
ensuring that all implementations behave uniformly and can
be scripted consistently. Because much of the functionality needed for
a Task Bench implementation is in the core library, implementations of
Task Bench are small: Our 15 Task Bench implementations range from 88
to 1500 lines, with several hundred lines being
typical. Listings~\ref{lst:compute-kernel} and \ref{lst:code-sample}
show excerpts from the Task Bench core, and the Dask implementation,
respectively. Only the code in Listing~\ref{lst:code-sample} is
implemented for each system, minimizing the work required for each additional system.
} % zap

>>>>

\zap{
Despite its generality, Task Bench is easy to implement, making it
tractable to develop a suite of high-quality implementations. The central aspects of Task Bench, such as generating
task graphs and enumerating dependencies, are encapsulated in a core
library that is shared among all the Task Bench implementations. The
core library also includes implementations of the kernels, ensuring
that the kernels are identical in all systems, eliminating a potential
source of performance disparity that can be a pitfall for
implementations of mini-apps. Finally, the core library manages
parsing input parameters and displaying results,
ensuring that all implementations behave uniformly and can
be scripted consistently. Because much of the functionality needed for
a Task Bench implementation is in the core library, implementations of
Task Bench are small: our 15 Task Bench implementations range from 88
to 1500 lines, with several hundred lines being
typical. Listings~\ref{lst:compute-kernel} and \ref{lst:code-sample}
show excerpts from the Task Bench core, and the Dask implementation,
respectively. Only the code in Listing~\ref{lst:code-sample} is
implemented for each system, minimizing the work required for each additional system.
} % zap

### 2019-11-22 5_evaluation.tex
Uncapitalize after colon.

One question when considering different programming
systems is: How much overhead does the system add? This question is tricky to answer directly because some systems introduce
overhead \emph{inline} (i.e., by running system internal processes on
the same cores as application tasks), while other systems introduce
overhead \emph{out-of-line} (i.e., by dedicating one or more cores
solely to runtime use). Some systems, like Charm++, Realm, and Regent,
support both configurations.

@@

Our MPI+CUDA implementation uses an offload model in which data is copied to and from the GPU on each step. We test
two configurations: \lstinline{w1} uses 1 task per GPU, whereas
\lstinline{w4} overdecomposes by $4\times$, using 4 MPI
ranks per GPU to push work to the GPU in parallel.
\lstinline{w4} achieves higher FLOP/s but
drops more rapidly at smaller problem sizes, due to the overhead of
scheduling $4\times$ as many CUDA kernel launches. In either case, the
GPU requires more work to achieve high performance, and the overhead
of copying data dominates at small task
granularities, where the CPU achieves higher
performance. While Figure~\ref{fig:cuda-efficiency} is not couched in
terms of METG (as peak performance on CPU and GPU are very
different), the conclusion here is similar to
Section~\ref{subsec:scalability}: The cost of sending data and
tasks to the GPU imposes a higher task granularity to achieve
the same efficiency than running on the CPU, reducing the advantage at small task granularities of
very lightweight mechanisms such as those in MPI.

>>>>

One question when considering different programming
systems is: how much overhead does the system add? This question is tricky to answer directly because some systems introduce
overhead \emph{inline} (i.e., by running system internal processes on
the same cores as application tasks), while other systems introduce
overhead \emph{out-of-line} (i.e., by dedicating one or more cores
solely to runtime use). Some systems, like Charm++, Realm, and Regent,
support both configurations.

@@

Our MPI+CUDA implementation uses an offload model in which data is copied to and from the GPU on each step. We test
two configurations: \lstinline{w1} uses 1 task per GPU, whereas
\lstinline{w4} overdecomposes by $4\times$, using 4 MPI
ranks per GPU to push work to the GPU in parallel.
\lstinline{w4} achieves higher FLOP/s but
drops more rapidly at smaller problem sizes, due to the overhead of
scheduling $4\times$ as many CUDA kernel launches. In either case, the
GPU requires more work to achieve high performance, and the overhead
of copying data dominates at small task
granularities, where the CPU achieves higher
performance. While Figure~\ref{fig:cuda-efficiency} is not couched in
terms of METG (as peak performance on CPU and GPU are very
different), the conclusion here is similar to
Section~\ref{subsec:scalability}: the cost of sending data and
tasks to the GPU imposes a higher task granularity to achieve
the same efficiency than running on the CPU, reducing the advantage at small task granularities of
very lightweight mechanisms such as those in MPI.
